The title

### 2018-02-23 writeup.Rmd
initial writup

@@

* discussing the ways people in tha past have measured the "implicature rate".

@@

* data exclusion? we don't expect any.

@@

* how are we choosing the sample size?

>>>>

* In a truth-value judgment task, how do we know whether an interpretation is literal or the result of an implicature computation?

Traditional Linking Hypotheses:
* If an implicature is calculated, the participant chooses a Non-True/Right response
* If an implicature is calculated, the participant chooses the Wrong/False response
* If an implicature is calculated, the participant chooses the lower end of the scale (2: wrong/False, 3: wrong, 4: wrong/kinda-wrong, 5: wrong/kinda-wrong)

Questions:
* Do these linking hypotheses give us different measures of implicature computation?
* If they do differ, which one is most stable?

Alternative Linking Hypothesis:
* RSA: Response behavior across conditions (utterance-card combinations) and dependent measures can be predicted by a linking hypothesis that assumes that participants are behaving like soft-optimal RSA speakers and provide a particular response (eg TRUE) to an utterance u if the RSA speaker probability of u (given the card) is within a particular probability interval (eg, within the interval [theta, 1]).

* Differences between traditional approaches and RSA: 1. The traditional linking hypotheses are based on a binary implicature/literal theory of pragmatic reasoning but RSA gives a continuous measure of pragmatic reasoning and allows for better predicting response behavior with multiple options.

@@

* discussing the ways people in tha past have measured the "implicature rate".
* it seems like the literature takes the n(not-True)/n(Total) as the proporition of responses caused by implicature calculation
* BUT, I remember that Jesse Snedeker said it's NOT n(not-True)/n(Total) but it is n(False)/n(Total)
* However, this is probably not a consensus in the field because Katsos & Bishop consider the mid-point response "big" on the scale small-big-huge (strawberry) to be the result of implicture caculation

* what is the most common measure of "implicature rate" in the literature?
Binary True/False: Noveck 2001, 
Ternary: Katsos & Bishop 2011

@@

* No data will be excluded.

@@

* how are we choosing the sample size? We went for a 20 per cell number. based on?
